Webscraping my data 1

### 2024-09-20 RQdraft3.Rmd
makingfilesw3

---
title: "week3 - class RSelenium"
author: "Verooo"
date: "2024-09-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

---

@@

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```

# see: https://jochemtolsma.github.io/webscraping/12scholars.html#13_necessary_packages
```{r}
# start with clean workspace
rm(list = ls())

# install.packages("RSelenium")
library(RSelenium)

# Web Driving with R Silenium

```
# citing openalexR in paper!
If you use openalexR in research, please cite: (Priem, Piwowar, and Orr 2022)

>>>>

---
title: "RQ draft 3"
author: "Verooo"
date: "2024-09-20"
output: html_document
---

@@

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### 2024-09-20 webscraping1.Rmd
makingfilesw3

---
title: "_SNASS tutorial"
author: "TreesDude"
date: "2024-09-04"
output: html_document
---

@@

```{r token}
#install.packages("gitcreds")
# gitcreds::gitcreds_set()
```

```{r}
# TO MAKENEW CHUNKS: ctrl + Alt + i

```

```{r}
########################### Title: Introducation to R for SNA Author: J Tolsma version: 30-10-2019

# start with clean workspace
rm(list = ls())

# install.packages I will need later here
install.packages("installr")  # you  first install packages
install.packages("foreign")
require(foreign)  # used to read in spss data files
require(tidyverse)

# define workdirectory, note the double backslashes
setwd("C:\Users\Vero\OneDrive - Radboud Universiteit\Documents\GitHub\labjournal")  # change to your own workdirectory
```

```{r}
# ignore the warnings ?read.spss note that I have saved the data files in a folder called
# 'addfiles'.

cv08 <- foreign::read.spss("addfiles\\Cultural_Changes_2008.sav", use.value.labels = T, to.data.frame = T)
cv10 <- foreign::read.spss("addfiles\\Cultural_Changes_2010.sav", use.value.labels = T, to.data.frame = T)

# normally I think setting use.value.labels=F is more convenient. Thus lets load the data again but
# now without labels
cv08_nolab <- foreign::read.spss("addfiles\\Cultural_Changes_2008.sav", use.value.labels = F, to.data.frame = T)
cv10_nolab <- foreign::read.spss("addfiles\\Cultural_Changes_2010.sav", use.value.labels = F, to.data.frame = T)

# finally, import the data using haven
cv08_haven <- haven::read_spss("addfiles\\Cultural_Changes_2008.sav")
cv10_haven <- haven::read_spss("addfiles\\Cultural_Changes_2010.sav")
```

>>>>

---
title: "Webscraping my data 1"
author: "Verooo"
date: "2024-09-20"
output: html_document
---

@@
